\documentclass[12pt]{article}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{geometry}
\geometry{a4paper, margin=1in}

\title{Intro to AI \\ Homework Assignment 1}
\author{Nikita Zagainov DSAI-01}
\date{\today}

\begin{document}

\maketitle

\section{Implementation Details}
\subsection{A Star Algorithm}
The code submitted to the assignment is an implementation of Agent that uses A*
algorithm to find best path to the goal. The implementation uses Dijkstra's
algorithm to traverse the map, the heuristic function is implemented as
Manhattan distance between the current position and the keymaker position. Only
heuristic function is used to estimate the cost of the path to the goal. This
is the only modification of the A* algorithm that was made to the
implementation.

\subsection{Backtracking Algorithm}
The code submitted to the assignment is an implementation of Agent that uses
backtracking algorithm to find best path to the goal. The implementation uses
BFS to traverse the map considering known threats, and whenever new information
is available on dangers on built path, the agent backtracks to the last known
safe position and rebuilds the path to the goal. No significant modifications
were made to the backtracking algorithm.

\subsection{Code}
\href{https://github.com/V1adych/itai_assignment_1}{Link to the code repository}

\section{Evaluation results}
The agents were evaluated on 1000 randomly generated maps below is the summary
of the results:

\begin{table}[h!]
    \centering
    \begin{tabular}{|c|c|c|}
        \hline
        \textbf{Metric}                           & \textbf{A* Algorithm}  & \textbf{Backtracking Algorithm} \\ \hline
        Mean Execution Time (s)                   & 0.00022995710372924804 & 0.0048852698802948              \\ \hline
        Std Execution Time (s)                    & 0.0007183165074499156  & 0.011766218056042806            \\ \hline
        Var Execution Time (s\textsuperscript{2}) & 5.159786048750448e-07  & 0.00013844388734234774          \\ \hline
        Mean Moves                                & 10.298                 & 10.48                           \\ \hline
        Std Moves                                 & 6.413204815067112      & 6.161623162771317               \\ \hline
        Var Moves                                 & 41.12919599999999      & 37.9656                         \\ \hline
        Win Fraction                              & 0.91                   & 0.915                           \\ \hline
    \end{tabular}
    \caption{Evaluation results of A* and Backtracking algorithms}
    \label{tab:evaluation_results}
\end{table}
As can be seen from the table, algorithm do not have big
statistical difference in terms of mean moves and win fraction. However, the
execution time of the A* algorithm implementation provided is significantly
lower than the execution time of the backtracking algorithm.

\section{Conclusion}
This assignment solution provides two implementations of the agent that can
solve the problem of path finding. Some modifications were made to the A*
algorithm to make it work with the problem. The backtracking algorithm was
implemented without any modifications. The evaluation results show that the A*
algorithm has slightly better performance in terms of execution time, but both
algorithms show approximately the same performance in terms of mean moves and
win fraction.
\end{document}